Figures to insert in text

### 2018-03-12 Chapters/sdm-critical-distance.tex
New SDM image
crit-distance

For details and the proof of this equation, see \citet{brogliato2014sparse}. Although Kanerva has found a formula for $\phi(d)$ through an unsolved integral, and \citet{de1995geometrical} has proposed another way to calculate $\phi(d)$, we have used our framework to estimate the values of $d$. In order to do that, we used a Monte Carlo approach, generating many pair of random bitstrings $d$ bits away from them and calculating the average number of shared hard-locations between them. The code is available in the ``Calculate critical distance'' notebook \citep{sdmframework}.

@@

As we can easily notice, we got exactly the same curve as Kanerva. This question has been intriguing us since then and we are still looking for a better explanation then ``attractors''.

@@

%\begin{figure}[h]
%\centering\includegraphics[width=0.8\textwidth]{images02/sdm-10000w-notX-table-7-2.png}
%\caption{This graph shows the interaction effects more clearly.  As we include an opposite bitstring, one can see the accelerating effects towards convergence to both attractors: the origin and the opposite. Here we have the exact same configuration of Figure \ref{sdm-10000w-table-7-2}, with the addition of the single opposite attractor.
%\label{sdm-10000w-notX-table-7-2}}
%\end{figure}

>>>>

For details and the proof of this equation, see \citet{brogliato2014sparse}. Although Kanerva has found a formula for $\phi(d)$ through an unsolved integral, and \citet{de1995geometrical} have proposed another way to calculate $\phi(d)$, we have used our framework to estimate the values of $d$. In order to do that, we used a Monte Carlo approach, generating many pair of random bitstrings $d$ bits away from them and calculating the average number of shared hard-locations between them. The code is available in the ``Calculate critical distance'' notebook \citep{sdmframework}.

@@

As we can easily notice, we got exactly the same curve as Kanerva. This question has been intriguing us since then and we are still looking for a more analytic explanation then merely interference from the other written attractors.

@@

%\begin{figure}[h]
%\centering\includegraphics[width=0.8\textwidth]{images02/sdm-10000w-notX-table-7-2.png}
%\caption{This graph shows the interaction effects more clearly.  As we include an opposite bitstring, one can see the accelerating effects towards convergence to both attractors: the origin and its polar opposite. Here we have the exact same configuration of Figure \ref{sdm-10000w-table-7-2}, with the addition of the single opposite attractor.
%\label{sdm-10000w-notX-table-7-2}}
%\end{figure}
